Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-27 be.tex
analytics...

Using equations~\eqref{eq:enConsInt},~\eqref{eq:massFlux},
and~\eqref{eq:Phi}, we may obtain an expression for the enthalpy,
$\ke+\gammaf \frac{p}{\rho}$ of the gas inside of the break radius
$\rb$. {\bf AG: 2s with question marks would not be included if the $G
\Mstar/r$ }

\begin{align}
&\frac{v^2}{2}+\gammaf \frac{p}{\rho} = \frac{G \Mbh}{x \rs} + \frac{G
  M_\star}{x \rs} - U_o \frac{x^{2-\delta}-1}{2-\delta}\nonumber\\
&-U_o\left[\frac{1}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
&+\frac{v_w^2}{2}-\frac{G \Mbh}{2 r_s} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1} -\frac{G M_\star}{2? r_s} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
\end{align}

@@

\begin{multline}
  \frac{v^2}{2}+\gammaf \frac{p}{\rho}
=\frac{G \Mbh}{\rs} 
\biggl[
  \zeta^2 w^{\frac{1}{3 -\delta}}+\frac{1}{x}+\frac{w}{x}
  -\frac{1}{2} \frac{3-\delta}{2-\delta} \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
  -w \frac{3 -\delta}{2 -\delta} x^{2 -\delta}
  -w \frac{(2-\delta)(3-\delta)-2?(3-\beta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
\biggr].
\label{eq:enthAnal}
\end{multline}

Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta$ is
the ratio of the extra heating rate to the stellar velocity in of the
influence radius $\rsoi$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
$\delta$ is the power law slope of the stellar density profile inside
of the break radius, $\rb$.

>>>>

Using equations~\eqref{eq:enConsInt},~\eqref{eq:massFlux},
and~\eqref{eq:Phi}, we may obtain an expression for the enthalpy,
$\ke+\gammaf \frac{p}{\rho}$ of the gas inside of the break radius
$\rb$.

\begin{align}
  &\frac{v^2}{2}+\gammaf \frac{p}{\rho} = \frac{G \Mbh}{x \rs} +
  \frac{G
    M_\star}{x \rs} - U_o \frac{x^{2-\delta}-1}{2-\delta}\nonumber\\
  &-U_o\left[\frac{1}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
  &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
  \frac{1-2\delta}{2(\delta+1)} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
  \nonumber\\
  &-\frac{G M_\star}{r_s}
  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
\end{align}

@@

\begin{multline}
  \frac{v^2}{2}+\gammaf \frac{p}{\rho}
=\frac{G \Mbh}{\rs} 
\biggl[
  \frac{3}{2} \zeta^2 w^{\frac{1}{3 -\delta}}+\frac{1}{x}+\frac{w}{x}
  -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
  -w \frac{3 -\delta}{2 -\delta} x^{2 -\delta}
  -w \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
\biggr].
\label{eq:enthAnal}
\end{multline}

Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta=\sqrt{(v_w^2+\sigma_0^2)/\sigma_0}$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
$\delta$ is the power law slope of the stellar density profile inside
of the break radius, $\rb$.
